%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

\begin{cvparagraph}
    $^*$ denotes the authors are co-first authors
\end{cvparagraph}

\newif\ifshowcontent % 새로운 조건변수 생성
\showcontentfalse

\cvsubsection{International Journal}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\newcommand{\hyungtaelim}{\underline{Hyungtae Lim}}

\begin{pubSubsectionNum}
    \item {\hyungtaelim, Beomsoo Kim, Daebeom Kim, and Hyun Myung, ``Quatro++: Robust Global Registration Exploiting Ground Segmentation for Loop Closing in LiDAR SLAM,'' \textit{Int. J. Robot. Res. (IJRR)}, 2023 (Under revision)}
    \item {\hyungtaelim, Seungjae Lee, Minho Oh, Changki Sung, Byeongho Yu, Dong-Uk Seo, and Hyun Myung, ``Patchwork2: Fast and Outlier-Robust Cascaded Ground Segmentation for Terrestrial Robots,'' \textit{IEEE Trans. Robot. (T-RO)}, 2023 (Under revision)}
    \item Alex Junho Lee, Seungwon Song, \hyungtaelim, Woojoo Lee, and Hyun Myung, ``$(LC)^2$: LiDAR-Camera Loop Constraints For Cross-Modal Place Recognition,'' \textit{IEEE Robot. Automat. Lett. (RA-L)}, vol. 8, no. 6, pp. 3589--3596, 20th, Apr. 2023
    \item DongKi Noh, Changki Sung, Teayoung Uhm, WooJu Lee, \hyungtaelim, Jaeseok Choi, Kyuewang Lee, Dasol Hong, Daeho Um, Inseop Chung, Hochul Shin, MinJung Kim, Hyoung-Rock Kim, SeungMin Baek, and Hyun Myung, ``X-MAS: Extremely Large-Scale Multi-Modal Sensor Dataset for Outdoor Surveillance in Real Environments,'' \textit{IEEE Robot. Automat. Lett. (RA-L)}, vol. 8, no. 2, pp. 1093–-1100, 12th Jan. 2023
    \item Seungwon Song, \hyungtaelim, Alex Junho Lee, and Hyun Myung, ``DynaVINS: A Visual-Inertial SLAM for Dynamic Environments,'' \textit{IEEE Robot. Automat. Lett. (RA-L)}, vol. 7, no. 4, pp. 11523-11530, 31st Oct. 2022
    \item Minho Oh$^*$, Euigon Jung$^*$, \hyungtaelim, Wonho Song, Sumin Hu, Eungchang Mason Lee, Junghee Park, Jaekyung Kim, Jangwoo Lee, and Hyun Myung, ``TRAVEL: Traversable Ground and Above-Ground Object Segmentation Using Graph Representation of 3D LiDAR Scans,'' \textit{IEEE Robot. Automat. Lett. (RA-L)}, vol. 7, no. 3, pp. 11523--11530, 13th Jun. 2022 \textbf{Won 2022 IEEE RA-L Best Paper Award}
    \item Seungwon Song, \hyungtaelim, and Hyun Myung, ``G2P-SLAM: Generalized RGB-D SLAM Framework for Mobile Robots in Low-Dynamic Environments,'' \textit{IEEE Access}, vol. 10, pp. 21370--21383, 11th Feb. 2022
    \item Changki Sung, Seulgi Jeon, \hyungtaelim, and Hyun Myung, ``What If There Was No Revisit? Large-Scale Graph-based SLAM with Traffic Sign Detection in an HD Map Using LiDAR Inertial Odometry,'' \textit{J. Intell. Serv. Robot.}, pp. 1--10, 25th Nov. 2021
    \item \hyungtaelim, Hanseok Ryu, Matthew Rhudy, Dongjin Lee, Dongjin Jang, Changho Lee, Young-min Park, Wonkeun Youn, and Hyun Myung, ``Deep Learning-Aided Synthetic Airspeed Estimation of UAVs for Analytical Redundancy with a Temporal Convolutional Network,'' \textit{IEEE Robot. Automat. Lett. (RA-L)}, vol. 7, no. 1, pp. 17--24, 1st Oct. 2021
    \item \hyungtaelim, Minho Oh, and Hyun Myung, ``Patchwork: Concentric Zone-Based Region-Wise Ground Segmentation With Ground Likelihood Estimation Using a 3D LiDAR Sensor,'' \textit{IEEE Robot. Automat. Lett. (RA-L) with IROS}, vol. 6, no. 4, pp. 6458--6465, 28th Jun. 2021
    \item Wonkeun Youn$^{*}$, \hyungtaelim$^{*}$, Hyoung Sik Choi, Matthew B. Rhudy, Hyeok Ryu, Sungyug Kim, and Hyun Myung, ``State Estimation of HALE UAV With Deep Learning-Aided Virtual AOA/SSA Sensor for Analytical Redundancy,'' \textit{IEEE Robot. Automat. Lett. (RA-L)}, vol. 6, no. 3, pp. 5276--5283, 19th Apr. 2021
    \item \hyungtaelim, Sungwon Hwang, and Hyun Myung, ``ERASOR: Egocentric Ratio of Pseudo Occupancy-Based Dynamic Object Removal for Static 3D Point Cloud Map Building,'' \textit{IEEE Robot. Automat. Lett. (RA-L) with ICRA}, vol. 6, no. 2, pp. 2272--2279, 23rd Feb. 2021

\end{pubSubsectionNum}

\cvsubsection{International Conference}

\begin{pubSubsectionNum}
    \item Jinwoo Jeon, Byeongho Yu, \hyungtaelim, and Hyun Myung, ``Seeing Without Seeing: Improving Deep Inertial Odometry by Leveraging Virtual Inertial Flow,'' in \textit{CVF Int. Conf. Comput. Vis. (ICCV)}, 2023 (Submitted)
    \item Wooju Lee, Dasol Hong, \hyungtaelim, and Hyun Myung, ``Object-Aware Domain Generalization for Object Detection,'' in \textit{CVF Int. Conf. Comput. Vis. (ICCV)}, 2023 (Submitted)
    \item Dong-Uk Seo, \hyungtaelim, Eungchang Mason Lee, Hyunjun Lim, and Hyun Myung, ``Enhancing Robustness of Line Tracking Through Semi-Dense Epipolar Search in Line-based SLAM,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, 2023 (Submitted)
    \item \hyungtaelim, Lucas Nunes, Benedikt Mersch, Xieyuanli Chen, Jens Behley, Hyun Myung, and Cyrill Stachniss, ``Instance-Aware Robust 3D Mapping of the Static World in Dynamic Scenes,'' in \textit{Robotics: Science and Systems~(RSS)}, 2023 (Accepted. To appear)
    \item \hyungtaelim, Kawon Han, Gunhee Shin, Giseop Kim, Songcheol Hong, and Hyun Myung, ``ORORA: Outlier-Robust Radar Odometry,'' in \textit{Proc. IEEE Int. Conf. Robot. Automat. (ICRA)}, 2023 (Accepted. To appear)
    \item Alex Junho Lee, \hyungtaelim, Minho Oh, Wonho Song, and Hyun Myung, ``Volumetric Vegetation Monitoring From LiDAR Scans With Ground Estimation,'' in \textit{Proc. Int. Conf. Control, Automat. Syst. (ICCAS)}, Busan, Republic of Korea, 27 Nov.-1 Dec. 2022, pp. 1378--1379
    \item Seungjae Lee$^*$, \hyungtaelim$^*$, and Hyun Myung, ``Patchwork++: Fast and Robust Ground Segmentation Solving Partial Under-Segmentation Using 3D point cloud,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, Kyoto, Japan, 22-27 Oct. 2022, pp. 13276--13283
    \item Sumin Hu, Yeeun Kim, \hyungtaelim, Alex Junho Lee, and Hyun Myung, ``eCDT: Event Clustering for Simultaneous Feature Detection and Tracking,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, Kyoto, Japan, 22-27 Oct. 2022, pp. 3808--3815
    \item Dong-Uk Seo$^*$, \hyungtaelim$^*$, Seungjae Lee, and Hyun Myung, ``PaGO-LOAM: Robust ground- optimized LiDAR odometry,'' in \textit{Proc. Int. Conf. Ubiquti. Robot. (UR)}, Jeju, Republic of Korea, 4-6 Jul. 2022, pp. 1--7
    \item \hyungtaelim, Suyong Yeon, Soohyun Ryu, Yonghan Lee, Youngji Kim, Jaeseong Yun, Euigon Jung, Donghwan Lee, and Hyun Myung, ``A Single Correspondence Is Enough: Robust Global Registration to Avoid Degeneracy in Urban Environments,'' in \textit{Proc. IEEE Int. Conf. Robot. Automat. (ICRA)}, Philadelphia, USA, 23-27 May 2022, pp. 8010--8017
    \item Sungwon Hwang, \hyungtaelim, and Hyun Myung, ``Equivariance-Bridged SO(2)-Invariant Representation Learning Using Graph Convolutional Network,'' in \textit{Proc. British Machine Vis. Conf. (BMVC)}, Virtual, 22-25 Oct. 2021
    \item Hyungyu Lee, Myeongwoo Jeong, Chanyoung Kim, \hyungtaelim, Changgue Park, Sungwon Hwang, and Hyun Myung, ``Low-level Pose Control of Tilting Multirotor for Wall Perching Tasks Using Renforcement Learning,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, Praque, Czech (Virtual), 27 Sep.-1 Oct. 2021, pp. 9669--9676
    \item Eungchang Mason Lee, Junho Choi, \hyungtaelim, and Hyun Myung, ``REAL: Rapid Exploration With Active Loop-Closing Toward Large-Scale 3D Mapping Using UAVs,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, Praque, Czech (Virtual), 27 Sep. - 01 Oct. 2021, pp. 4194--4198
    \item \hyungtaelim, Hyeonjae Gil, and Hyun Myung, ``MSDPN: Monocular Depth Prediction With Partial Laser Observation Using Multi-stage Neural Networks,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, Las Vegas, USA (Virtual), 24 Oct.-24 Dec. 2020, pp. 10750--10757
    \item \hyungtaelim, Sungwon Hwang, Sungjae Shin, and Hyun Myung, ``Normal Distributions Transform is Enough: Real-Time 3D Scan Matching for Pose Correction of Mobile Robot Under Large Odometry Uncertainties,'' in \textit{Proc. Int. Conf. Control, Automat. Syst. (ICCAS)}, Busan, Republic of Korea, 13-16 Oct. 2020, pp. 1155--1161, \textbf{Received Student Best Paper Award}
    \item \hyungtaelim, Changgue Park, and Hyun Myung, ``RONet: Real-Time Range-Only Indoor Localization via Stacked Bidirectional LSTM with Residual Attention,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, Macau, China, 4-8 Nov. 2019, pp. 3241--3247
    \item Jungmo Koo, Changgue Park, \hyungtaelim, and Hyung Myung, ``Light-Weight Deep Neural Networks for Multi-Target Classification,`` in \textit{Proc. Int. Conf. Control, Automat. Syst. (ICCAS)}, Jeju, Republic of Korea, Oct. 2019
    \item Jieum Hyun, Taekjun Oh, \hyungtaelim, and Hyung Myung, ``UWB-Based Indoor Localization Using Ray-Tracing Algorithm,'' in \textit{Proc. Int. Conf. Ubiquti. Robot. (UR)}, Hawaii, USA, 24-27 Jun. 2019, pp. 98--101
    \item \hyungtaelim, Jungmo Koo, Jieum Hyun, and Hyung Myung, ``Effective Indoor Robot Localization by Stacked Bidirectional LSTM Using Beacon-Based Range Measurements,'' in \textit{Proc. Int. Conf. Robot Intell. Tech. Applications (RiTA)}, Putrajaya, Malaysia, 16-18 Dec. 2018, pp. 144--151
    \item \hyungtaelim, Jungmo Koo, Jieum Hyun, and Hyun Myung, ``Recurrent Neural Networks for Range-Based Indoor Robot Localization,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, Madrid, Spain, Oct. 2018
\end{pubSubsectionNum}

%
%\begin{pubSubsectionNum}{International Conference Proceedings}
%  \item \bibentry{jeon-2023-iccv}
%  \item \bibentry{lee-2023-iccv}
%  \item \bibentry{seo-2023-iros}
%  \item \bibentry{lim-2023-rss}
%  \item \bibentry{lim-2022-orora}
%  \item \bibentry{lee-2022-volumetric}
%  \item \bibentry{lee-2022-patchpp}
%  \item \bibentry{hu-2022-ecdt}
%  \item \bibentry{lim-2022-pago}
%  \item \bibentry{lim-2022-quatro}
%  \item \bibentry{sungwon-2021-bmvc}
%  \item \bibentry{hyungyu-2021-iros}
%  \item \bibentry{eungchang-2021-iros}
%  % 2020
%  \item \bibentry{htlim-2020-iros}
%  \item \bibentry{htlim-2020-iccas}
%  \item \bibentry{htlim-2019-iros}
%  \item \bibentry{jmkoo-2019-iccas}
%  \item \bibentry{jieumhyun-2019-ur}
%  \item \bibentry{htlim-2018-rita}
%  \item \bibentry{htlim-2018-iros}
%\end{pubSubsectionNum}
%
