%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience (Including Internship)}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {LG Electronics Co. Ltd.} % Job title
    {Ouside Expert of CTO Division of LG Electronics Co. Ltd.} % Organization
    {Republic of Korea} % Location
    {Mar. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Was in charge of introducing state-of-the-art SLAM technologies and suggesting the direction of future technologies for mobile robots.
        \item Gave a lecture entitled \textit{"Introduction of the latest SLAM technology trends and Semantic SLAM"}
      \end{cvitems}
    }

  \cventry
    {StachnissLab} % Job title
    {Visiting Scholar} % Organization
    {Bonn, Germany} % Location
    {Nov. 2022 - Feb. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item After defense of my dissertation, I visited Prof. Cyrill Stahcniss' lab
        \item Was in charge of improved version of static map building
        \item Submitted and accepted a paper to RSS 2023 titled \textit{ERASOR2}.
        \item Code is available at \href{https://github.com/url-kaist/ERASOR2}{\texttt{https://github.com/url-kaist/ERASOR2}}
      \end{cvitems}
    }

  \cventry
    {NAVER LABS} % Job title
    {Research Intern} % Organization
    {Gyeonggi-Do, Republic of Korea} % Location
    {Apr. 2022 - Sep. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Was a Ph.D research intern
        \item Was in charge of robust global registration using 3D point cloud captured by a LiDAR sensor called \textit{Quatro}.
        \item Submitted and accepted a paper to IEEE ICRA 2022.
        \item Code is available at \href{https://github.com/url-kaist/Quatro}{\texttt{https://github.com/url-kaist/Quatro}}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
